Supplemental Material: Multidimensional analysis and detection of informative features in human white matter

### 2021-01-25 reports/manuscript/sections/introduction.tex
Whitespace.

Non-invasive methods for measuring human brain structure and function have revolutionized our understanding of brain function. These measurements
have demonstrated that interactions between networks of brain regions give rise to coordinated information processing and to the complex adaptive behavior that characterizes human cognition. Diffusion-weighted Magnetic Resonance Imaging (dMRI) provides a unique view into the physical properties of the connections that comprise these networks, by sensitizing the measurement to the directional

@@

Methods for computational tract-tracing from diffusion MRI, or tractography, combine the estimates of fiber orientations in each voxel to form streamlines

@@

trajectory of major neural pathways among these streamlines~\cite{yeatman2012tract}.

@@

voxel to assess the physical properties of the white matter along specific pathways~\cite{Bells2011-cf}.

@@

% Different approaches can be taken to resolving this challenge. For
% example, Colby and colleagues \cite{colby2012} used a non-parametric resmapling approach to
% correct for family-wise error across the different possible comparisons
% \cite{Nichols2002-zu, Nichols2003-yy}.
% Based on tractometry, researchers may choose to compare different individuals to each other. This is usually done according to one of the following approaches:
% \begin{enumerate}
% \item Mass univariate approaches: In this approach

>>>>

Non-invasive methods for measuring human brain structure and function have
revolutionized our understanding of brain function. These measurements
have demonstrated that interactions between networks of brain regions give rise
to coordinated information processing and to the complex adaptive behavior that
characterizes human cognition. Diffusion-weighted Magnetic Resonance Imaging
(dMRI) provides a unique view into the physical properties of the connections
that comprise these networks, by sensitizing the measurement to the directional

@@

Methods for computational tract-tracing from diffusion MRI, or tractography,
combine the estimates of fiber orientations in each voxel to form streamlines

@@

trajectory of major neural pathways among these
streamlines~\cite{yeatman2012tract}.

@@

voxel to assess the physical properties of the white matter along specific
pathways~\cite{Bells2011-cf}.

@@

% Different approaches can be taken to resolving this challenge. For
% example, Colby and colleagues \cite{colby2012} used a non-parametric
% resmapling approach to
% correct for family-wise error across the different possible comparisons
% \cite{Nichols2002-zu, Nichols2003-yy}.
% Based on tractometry, researchers may choose to compare different individuals
% to each other. This is usually done according to one of the following
% approaches:
% \begin{enumerate}
% \item Mass univariate approaches: In this approach
